\RequirePackage{lineno}
%\documentclass[preprint,superscriptaddress,nofootinbib, notitlepage, double-spaced, showpacs,floatfix,longbibliography]{revtex4-1}
\documentclass[review]{elsarticle}
%\documentclass[twoside,12pt]{article}
%\linenumbers
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
\usepackage{rotating}
\usepackage{graphicx}% Include  files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epsfig}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{appendix}
%\usepackage{iopams}
\usepackage{mwe}
\usepackage{subfig}
\usepackage{lineno}
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax
\usepackage{amsmath}
\usepackage{geometry}
\newgeometry{vmargin={20mm}, hmargin={30mm,22mm}}
%Uncomment next line if AMS fonts required
\usepackage{times}  
%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%\usepackage[backend=biber,style=nature]{biblatex}
%\addbibresource{BeautyExp.bib}

%%%% new commands
\newcommand{\barb}{{\bar{b}}}
\newcommand{\barc}{{\bar{c}}}
\newcommand{\SNN}{$\sqrt{s_{NN}}=$ }
\newcommand{\sqrtsnn}{\ensuremath{\sqrt{s_{NN}}}\xspace}
\newcommand{\raa}{$R_{AA}~$}
\newcommand{\pt}{$p_{T}$}
\newcommand{\npart}{$N_{\rm Part}~$}
\newcommand{\Jpsi}{\ensuremath{J\hspace{-.08em}/\hspace{-.14em}\psi}\xspace} % J/Psi (no mass)
\newcommand{\qqbar}{\ensuremath{q \overline{q}\xspace}\xspace}
\newcommand{\QQbar}{\ensuremath{Q \overline{Q}\xspace}\xspace}
\newcommand{\pp}{{\ensuremath{pp}}\xspace}
\newcommand{\PgU}{\ensuremath{\Upsilon}\xspace}
\newcommand{\PgUa}{\ensuremath{\Upsilon\text{(1S)}}\xspace}
\newcommand{\PgUb}{\ensuremath{\Upsilon\text{(2S)}}\xspace}
\newcommand{\PgUc}{\ensuremath{\Upsilon\text{(3S)}}\xspace}
\newcommand{\fig}[1]{Fig.~\ref{#1}\xspace}
\newcommand{\tab}[1]{Tab.~\ref{#1}\xspace}
\newcommand{\pT}{p_{T}}
\newcommand{\sNN}{\sqrt{s_{_{NN}}}}


\newcommand{\jpsi}{\ensuremath{\mathrm{J}/\psi}\hspace {0.05in}} 
\newcommand{\ups}{\ensuremath{\Upsilon}\hspace {0.05in}}
\newcommand{\upsa}{\ensuremath{\Upsilon\mathrm{(1S)}}\hspace {0.05in}}
\newcommand{\upsb}{\ensuremath{\Upsilon\mathrm{(2S)}}\hspace {0.05in}}
\newcommand{\upsc}{\ensuremath{\Upsilon\mathrm{(3S)}}\hspace {0.05in}}
\newcommand{\upsbc}{\ensuremath{\Upsilon\mathrm{(2S+3S)}}\xspace}
\newcommand{\upsabc}{\ensuremath{\Upsilon\mathrm{(1S+2S+3S)}}\xspace}
\newcommand{\upsn}{\ensuremath{\Upsilon\mathrm{(nS)}}\xspace}
\newcommand{\doubleRatioUps}{\ensuremath{\left.(N_{\upsb}/N_{\upsa})_{\mathrm{Pb-Pb}}/(N_{\upsb}/N_{\upsa})_{\mathrm{pp}}\right.\xspace}}
\newcommand{\psiP}{\ensuremath{\psi\mathrm{(2S)}}\hspace {0.05in}}
\newcommand{\chic}{\ensuremath{\chi_c}\hspace {0.05in}}
\newcommand{\chib}{\ensuremath{\chi_b}\hspace {0.05in}}



\newcommand{\Qcal}{\ensuremath{\Phi\xspace}}
\newcommand{\ccbar}{\ensuremath{{c\overline{c}}}\xspace}
\newcommand{\bbbar}{\ensuremath{{b\overline{b}}}\xspace}

\newcommand{\sqrts}{\ensuremath {\sqrt{s}}\hspace {0.05in}}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}

\begin{document}
%\begin{frontmatter}
  \title{Production of bottomonia states in proton+proton and heavy ion collisions}
  \author[NPD]{Vineet Kumar}
  \author[NPD,HBNI]{Prashant Shukla}
  \author[UOC]{Abhijit Bhattacharyya\corref{mycorrespondingauthor}}
  \cortext[mycorrespondingauthor]{Corresponding author}
  \ead{abhattacharyyacu@gmail.com}
  \address[NPD]{Nuclear Physics Division, Bhabha Atomic Research Centre, Mumbai 400085, India}
  \address[HBNI]{Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400094, India}
  \address[UOC]{Department of Physics, University of Calcutta, 92, A. P. C. Road Kolkata-700009, India}
  \date{\today}



\fontsize{11}{15}
\selectfont


  
\begin{abstract}
    
 In this work, we review the experimental and theoretical developments of bottomonia
production in proton+proton and heavy ion collisions. Bottomonia production
process is proving to be one of the most robust processes to investigate the
fundamental aspects of Quantum Chromodynamics at both low and high temperatures.  
The LHC experiments in last decade have produced large statistics of
bottmonia states in wide kinematic range in various collision
systems. The bottomonia have three $\Upsilon$ S-states which are
reconstructed in dilepton invariant mass channel with high mass resolution by
LHC detectors and P-states are measured via their decay to S-states. 
We start with the details of measurements in proton+proton collisions and their
understanding in terms of various effective theoretical models. Here we cover both the
Tevatron and LHC measurements with $\sqrt{s}$ spanning from 1.8 TeV to 13 TeV. 
  The bottomonia states have particualrly been very good probes to understand
strongly interacting matter produced in heavy ion collisions. The Pb+Pb
collisions have been performed at various energies at LHC. This has enabled to
study the modification of bottominia yields as function of various parameters
and collision energy. At the same time, the improved results of bottomonia
production are available from RHIC experiments which have proven to be useful
for a quantitative comparison. 
 A systematic study of bottomonia production in p+p,
p+Pb and Pb+Pb have been very useful to understand the medium effects
in these collision systems. We review some if not all the models of bottomonia
evolution due to various processes in a large dynamically evolving medium and
discuss these in comparison with the measurements. 

\end{abstract}
  
  
%\maketitle 

\begin{keyword}
   Beauty, Quarkonium, Bottomonium, Hadron Collision, Heavy-Ion Collision, Quark-Gluon Plasma, LHC, RHIC
\end{keyword}
  

%\vspace{2pc}
%\noindent{\it Keywords}: Beauty, Quarkonium, Hadron Collision, Heavy-Ion Collision, Quark-Gluon Plasma, LHC, RHIC
 

\maketitle

\newpage

\tableofcontents


%\end{frontmatter}

\input{Introduction}
\input{BottPP}
\input{BottAAexp}
\input{BottAAthe}
\input{Conclusions}


%\section*{References}
%\printbibliography %% for biber
\bibliography{Bott1Review.bib}


\end{document}


